The Weakly Nonlinear Magnetorotational Instability

### 2016-09-02 paper/widegap_mri_paper.tex
added acknowledgements; NASA grants; fixed jso affiliation

%\title{Weakly Nonlinear Analysis of the Standard and Helical Magnetorotational Instabilities in a Taylor Couette Flow}
\title{The Weakly Nonlinear Magnetorotational Instability} % maybe this is punchier?
\author{Clark, S.E.\altaffilmark{1}}
\author{Oishi, J.S. \altaffilmark{2,}\altaffilmark{3}}
%\author{Mac Low, M.-M.\altaffilmark{1,}\altaffilmark{2}}
\altaffiltext{1}{Department of Astronomy, Columbia University, New York, NY} 
\altaffiltext{2}{Department of Astrophysics, American Museum of Natural History, New York, NY}
\altaffiltext{3}{Department of Physics, SUNY Farmingdale}

@@

\section{Acknowledgements}
NASA, NSF. The authors thank Mordecai Mac Low, Jeremy Goodman, John Krommes, etc for useful discussion.

>>>>

%\title{Weakly Nonlinear Analysis of the Standard and Helical Magnetorotational Instabilities in a Taylor Couette Flow}
\title{The Weakly Nonlinear Magnetorotational Instability} % maybe this is punchier?
\author{Clark, S.E.\altaffilmark{1}}
\author{Oishi, J.S. \altaffilmark{2,}\altaffilmark{3}}
%\author{Mac Low, M.-M.\altaffilmark{1,}\altaffilmark{2}}
\altaffiltext{1}{Department of Astronomy, Columbia University, New York, NY} 
\altaffiltext{2}{Department of Astrophysics, American Museum of Natural History, New York, NY}
\altaffiltext{3}{Department of Physics and Astronomy, Bates College}

@@

\section{Acknowledgements}
JSO acknowledges support from NASA grant 15-LWS15_2-0063. NSF. The authors thank Mordecai Mac Low, Jeremy Goodman, John Krommes, Geoff Vasil, etc for useful discussion.
